Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex

\changwan{explain roadnet and scale free graphs here}
To evaluate the capabilities of Finch in graph applications, we its performance for two fundamantal graph applications: Breadth-first search (BFS) and Bellman-Ford single-source shortest path. We For scale-free graphs where the distribution of node degrees follows a power-law distribution and a diameter is very short, direction-optimization~\cite{} is crucial to achiceve high-performance. Direction-optimized BFS uses push and pull traversal to efficiently explore graphs. Push traversal starts from the source node, pushing neighboring nodes into the queue. Pull traversal starts from the target node, exploring predecessors (parents). This approach uses early-break in pull traversal, which is used to terminate the traversal prematurely once the target node is encountered, to avoid unnecessary edge traversal.

>>>>

To evaluate the capabilities of Finch in graph applications, we its performance for two fundamantal graph applications: Breadth-first search (BFS) and Bellman-Ford single-source shortest path. We used graphs in GraphBLAS~\cite{}, which include road networks (SNAP/roadNet-CA and GAP/GAP-road) where node degrees are bounded and a diametr is very long and scale-free graphs (the others) where the distribution of node degrees follows a power-law distribution and a diameter is very short, direction-optimization~\cite{} is crucial to achiceve high-performance. Direction-optimized BFS uses push and pull traversal to efficiently explore graphs. Push traversal starts from the source node, pushing neighboring nodes into the queue. Pull traversal starts from the target node, exploring predecessors (parents). This approach uses early-break in pull traversal, which is used to terminate the traversal prematurely once the target node is encountered, to avoid unnecessary edge traversal.
